$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-02-01 paper/e6ssm-tuning-paper.tex
Added Adelaide pre-preprint number to paper, ADP-15-4/T906
Added brief acknowledgements to start with, should there be anyone else added to them?
Added in 2-loop betas for gauge couplings

\pacs{12.60.Jv, 11.30.Pb, 12.60.-i, 14.80.Bn}
\keywords{naturalness, fine tuning, supersymmetry}%Use showkeys class option if keyword
                              %display desired
\maketitle

@@

% Our conclusions: at low scales stops are not a big contributor,
% Z' causes a significant fine tuning in the E6SSM (dominant -> lower
% bound), chargino bounds will be important for fine tuning in the MSSM
% but not as much for the E6SSM, and possibly discuss different U(1)' charges.

@@

mixing, the two-loop $\beta$ functions for the gauge couplings read

@@

\beta_{g_1}^{(2)}&=\frac{2}{25},\label{eq:USSMg1BetaTwoLoop}\\

@@

\beta_{g_3}^{(1)}&=0,\label{eq:USSMg3BetaOneLoop}\\
\beta_{g_1'}^{(1)}&=g_1'^3\Sigma_{\tilde{Q}},\label{eq:USSMg1pBetaOneLoop}

@@

to denote the trace over the $U(1)'$ charges, and

@@

\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i\\
&=-3\tilde{Q}_1+3\tilde{Q}_2+3\tilde{Q}_d-3\tilde{Q}_D+3\tilde{Q}_e-3\tilde{Q}_L+3\tilde{Q}_Q-6\tilde{Q}_u+3\tilde{Q}_{\overline{D}}+\tilde{Q}_{\overline{H'}}-\tilde{Q}_{H'}.

@@

Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised.\\ \\

@@

&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [\tilde{Q}_1^2+\tilde{Q}_2^2+\left ( \tilde{Q}_2-\tilde{Q}_1\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}

>>>>

\pacs{12.60.Jv, 11.30.Pb, 12.60.-i, 14.80.Bn}
\keywords{naturalness, fine tuning, supersymmetry}%Use showkeys class option if keyword
                              %display desired
\preprint{ADP-15-4/T906}
\maketitle

@@

\acknowledgements
We would like to thank R. Nevzorov for many useful discussions and comments. DH would also like to thank A. Ismail and T. Rizzo. This work was supported by the University of Adelaide and by the ARC Centre of Excellence for Particle Physics at the Terascale.

@@

mixing, the two-loop $\beta$ functions for the relevant gauge couplings read

@@

\beta_{g_1}^{(2)}&=\frac{2}{25} g_1^3 \left(30 g_1'^2 \Pi_{\tilde{Q}}^Y-35 y_b^2+117 g_1^2+135 g_2^2+300 g_3^2-10 \Sigma _{\kappa }-15
   \Sigma _{\lambda }-65 y_t^2-45 y_{\tau }^2\right),\label{eq:USSMg1BetaTwoLoop}\\

@@

\beta_{g_2}^{(2)}&=\frac{2}{5} g_2^3 \left(5 g_1'^2 \Pi _{\tilde{Q}}^L-15 y_b^2+9 g_1^2+115 g_2^2+60 g_3^2-5 \Sigma _{\lambda }-15
   y_t^2-5 y_{\tau }^2\right),\label{eq:USSMg2BetaTwoLoop}\\
\beta_{g_1'}^{(1)}&=g_1'^3\Sigma_{\tilde{Q}},\label{eq:USSMg1pBetaOneLoop}\\
\beta_{g_1'}^{(2)}&=\frac{2}{5} g_1'^3 \left(-15 \Sigma _{\kappa } \left(\tilde{Q}_{\bar{D}}^2+\tilde{Q}_D^2+\tilde{Q}_S^2\right)-30
   y_b^2 \left(\tilde{Q}_d^2+\tilde{Q}_1^2+\tilde{Q}_Q^2\right)+120 g_3^2 \Pi _{\tilde{Q}}^C\right.\nonumber \\
&\quad{}-10 y_{\tau }^2
   \left(\tilde{Q}_e^2+\tilde{Q}_L^2+\tilde{Q}_1^2\right)+15 g_2^2 \Pi _{\tilde{Q}}^L+10 g_1'^2 \Pi _{\tilde{Q}}+6
   g_1^2 \Pi _{\tilde{Q}}^Y\nonumber\\
&\quad\left.{}-10 \Sigma _{\lambda } \left(\tilde{Q}_S^2+\tilde{Q}_1^2+\tilde{Q}_2^2\right)-30 y_t^2
   \left(\tilde{Q}_u^2+\tilde{Q}_2^2+\tilde{Q}_Q^2\right)\right).\label{eq:USSMg1pBetaTwoLoop}

@@

to denote the trace over the $U(1)'$ charges, along with

@@

\Sigma_{\tilde{Q}}^Y&=\sum_i \sqrt{\frac{5}{3}}Q_i^Y\tilde{Q}_i,\\
\Pi_{\tilde{Q}}&=\sum_i \tilde{Q}_i^4,\\
\Pi_{\tilde{Q}}^Y&=\sum_i \left ( \sqrt{\frac{5}{3}}Q_i^Y\right )^2\tilde{Q}_i^2,\\
\Pi_{\tilde{Q}}^L&=3\tilde{Q}_1^2+3\tilde{Q}_2^2+\tilde{Q}_{H'}^2+\tilde{Q}_{\overline{H'}}^2+3\tilde{Q}_L^2+9\tilde{Q}_Q^2,\\
\Pi_{\tilde{Q}}^C&=\tilde{Q}_d^2+\tilde{Q}_D^2+\tilde{Q}_{\overline{D}}^2+2\tilde{Q}_Q^2+\tilde{Q}_u^2.

@@

Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised. Similarly we have set
The corresponding $O(t^2)$ coefficients for the gauge couplings are simply
\begin{subequations}\label{eq:USSMGaugeOt2Coeffs}
b_{g_1}^{(2)}&=\frac{3456}{25}g_1^5,\label{eq:USSMg1Ot2Coeff}\\
b_{g_2}^{(2)}&=24g_2^5,\label{eq:USSMg2Ot2Coeff}\\
b_{g_1'}^{(2)}&=\frac{3}{2}g_1'^5\Sigma_{\tilde{Q}}^2.\label{eq:USSMg1pOt2Coeff}

@@

&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [\tilde{Q}_1^2+\tilde{Q}_2^2+\left ( \tilde{Q}_2-\tilde{Q}_1\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \}.\label{eq:USSMLambdaBetaTwoLoop}
